The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2025-11-04 SIGMA/SIGMA_submission/borel_reg_submission.tex
Add second author's contact info
Add space at the end of equations before punctuation

% Address of Second Author
\Address{$^{\rm b)}$~Address of Second Author, Country}
\EmailD{\href{mailto:email@address}{email@address}} % E-mail address of Second Author

@@

%
\section{Introduction}
%
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
You can often find a formal power series
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel_rescaled_ex}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em trans-monomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.\footnote{Trans-mononials can be of different kinds: for example, fractional powers of $z$ can appear in the exponential. In this paper, however, we will only deal with trans-monomials of the form $e^{-\alpha z}\,\series{\Phi}$ for $\alpha \in \C$.} Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution 
\begin{equation}
e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{6718464} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel_ex}
\end{equation}
and its constant multiples (see \cite[equation 10.40.1]{dlmf}). As another example, you might rewrite the integral
\begin{equation}\label{int:bessel_ex}
\Phi = \int_{\mathcal{C}} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du
\end{equation}
as
\[ e^{z}\, \frac{1}{2\sqrt{3}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{\sqrt{3}}{9} t + \frac{5}{72} t^2 - \frac{4\sqrt{3}}{243} t^3 + \frac{385}{31104} t^4 - \frac{7\sqrt{3}}{2187} t^5 + \frac{17017}{6718464} t^6 - \ldots \right] dt \]
using the substitution $\tfrac{1}{2} t^2 = 4u^3 - 3u + 1$. Na\"{i}vely integrating term by term, you again get the trans-monomial~\eqref{series:bessel_ex}, up to a constant.

@@

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a level~$1$ linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.\footnote{Calling a linear ODE {\em level~$1$} is a short way of saying that it has ``a single level, equal to $1$, at infinity.'' That means a certain Newton polygon associated with its singularity at infinity has exactly one positive-slope side, which has slope~$1$. In general, the {\em levels} of a linear ODE at a given singularity are the slopes of the positive-slope sides of the associated Newton polygon~\cite[Proposition~3.3.14]{diverg-resurg--ii}.} Equation~\eqref{eqn:bessel_rescaled_ex} is an example. More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form 
\[ \mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}), \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial that is non-zero at every root of $P$, and $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. We will restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}), and to the solutions associated with roots $-\alpha$ where $\tau_\alpha:=\frac{Q(-\alpha)}{P'(-\alpha)}$ is real and positive (see Theorem~\ref{thm:exist_uniq_ODE}).

The form of $\mathcal{P}$ derives from equation~2.2.3 of \cite[p.~105]{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$. Borel summation is more involved for the nonlinear ones, raising the question of whether our analysis generalizes.
%
\item Evaluating a one-dimensional {\em thimble integral}. Integral~\eqref{int:bessel_ex} is an example. More generally, we will consider integrals of the form
\begin{equation*}
I = \int_{\mathcal{C}}e^{-zf}\,\nu,
\end{equation*}
where $X$ is one-dimensional complex manifold; $f \maps X \to \C$ is a holomorphic function with isolated, non-degenerate critical points; $\nu \in \Omega^1(X)$ is holomorphic $1$-form on $X$, and $\mathcal{C}$ is {\em Lefschetz thimble}---a type of contour described in Section~\ref{sec:why_borel_thimble}. Under these conditions, $I$ is a holomorphic function of $z$.
\end{enumerate}
These two problems are closely linked. By playing with derivatives of a thimble integral, you can often find a linear ODE that the integral satisfies. Conversely, for many classical ODEs, there are useful bases of thimble integral solutions.
%
\subsection{Goals and Results}
%
We present the results, proofs, and examples in this paper with a few central goals in mind. Our first goal is to discuss Borel summability in a way that carefully separates the analytic and formal sides of the theory. In particular, we highlight results that can be proven in purely analytic ways, like Theorem~\ref{thm:exist_uniq_ODE} for level~$1$ ODEs and Lemma~\ref{lem:thimble_proj_formula} for thimble integrals.

@@

We are now ready to define a one-dimensional thimble integral precisely, at our desired level of generality.
\begin{definition}
Fix a one-dimensional complex manifold $X$; a translation surface $B$; and a holomorphic map $f \maps X \to B$ with isolated, non-degenerate critical points. A one-dimensional {\em thimble integral} has the form
\[ I_a = \int_{\mathcal{C}_a^\theta} e^{-zf}\,\nu, \]
where $\nu$ is a holomorphic $1$-form on $X$, $a$ is a critical point of $f$, and $\mathcal{C}^\theta_a$ is the Lefschetz thimble that runs through $a$ in direction $\theta$ with a chosen orientation. Since $I_a$ depends on the frequency coordinate $z$, it is a holomorphic function on the frequency domain.
\end{definition}
We will present a proof that one-dimensional thimble integrals are always Borel regular. The proof hinges on the following well-known formula, which can be used to express any one-dimensional thimble integral as a Laplace transform.
\begin{lemma}[adapted from {\cite[Section~3.3]{pham}}]\label{lem:thimble_proj_formula}
A function $\iota_a$ with $I_a = \laplace_{\zeta, \alpha}^\theta \iota_a$ is given by the {\em thimble projection formula}
\begin{equation}\label{eqn:formula}
    \iota_a = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right),
\end{equation}
where $\mathcal{C}_a^\theta(\zeta)$ is the part of $\mathcal{C}_a^\theta$ that goes through $f^{-1}([\alpha,\zeta e^{i\theta}])$.
\end{lemma}
Notice that the path $\mathcal{C}_a^\theta(\zeta)$ used in the lemma starts and ends in $f^{-1}(\zeta)$.

@@

In the path integral picture of quantum mechanics, which draws inspiration from wave optics, infinite-dimensional thimble integrals are supposed to give the expectation values of observable quantities. In this context, the integral's formal asymptotic expansion is often better-defined than the integral itself, so physicists use Borel summation, resurgence, and related techniques to assign the integral a value. For instance, in the two-dimensional, $\mathcal{N}=2$ supersymmetric QFTs given by Landau--Ginzburg theories, Cecotti and Vafa showed that instantons can be computed using Picard--Lefschetz formulas. Indeed, the so-called wall-crossing phenomenon is equivalent to the Stokes phenomenon for thimble integrals~\cite{Cecotti:1992rm}. Similarly, in complex Chern--Simons theory, the path integral can be studied by decomposing it into thimble integrals and then arguing as in finite dimension~\cite{gukov-marino-purtrov-resurgence,Witten}. Other examples can be found in~\cite{costin_kruskal,Garoufalidis--CS,GTM--CS,GGM,dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua,Berry_Howls,Berry1991,Howls97,Howls,pham1988resurgence,Unsal--resurgence-gauge}.
%
\subsubsection{Thimble integrals in geometry}
Thimble integrals can be used to explore the geometry of complex manifolds, and even to represent elements of a homology group. To see how this works, we first recall how the one-dimensional definition of a Lefschetz thimble arises from the general definition. Suppose that $f \maps X \to B$ is a holomorphic map from an $N$-dimensional complex manifold $X$ to a translation surface $B$. Consider a translation chart $\zeta$ on $B$ and a non-degenerate critical point $a \in X$ that $f$ sends to $\zeta = \alpha$. Near $a$, we can always find coordinates $t_1, \ldots, t_N$ on $X$ with
\[ f^*\zeta = \alpha + e^{i \theta} (t_1^2 + \ldots + t_N^2). \]
When the ray $\mathcal{J}_{\zeta, \alpha}^\theta$ avoids the other critical values of $f$, each such coordinate system defines a Lefschetz thimble: the oriented real-analytic submanifold where $t_1, \ldots, t_N$ are real. There are many such coordinate systems, but they are all related by local holomorphic maps from $X$ to the complex orthogonal group $O_N(\C)$. Since $O_N(\C)$ has only two connected components, distinguished by the sign of the determinant, a Lefschetz thimble is determined up to homotopy and orientation by the critical point $a$ and the direction $\theta$. When $N = 1$, the homotopy freedom disappears, because $O_1(\C)$ is the discrete group $\{\pm 1\}$.

@@

At an ordinary point, we can define $z$ simply as the map
\begin{equation*}
\begin{split}
z \maps T^*_bB & \to \C \\
\lambda\big|_b & \mapsto 1.
\end{split}
\end{equation*}
To generalize $z$ to branch points, though, we need a more sophisticated definition. Recall that $T^*_bB = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$. Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*_bB^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$. When $b$ is an ordinary point, the translation parameter $\zeta_b$ that vanishes at $b$ represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda\big|_b$. In general, $\zeta_b$ represents a nonzero element of $\van_b^n / \van_b^{n+1}$, where $2\pi n$ is the cone angle at $b$. We define $z$ as the isomorphism
\begin{equation*}\begin{split}
z \maps \van_b^n / \van_b^{n+1} & \to \C \\
\zeta_b + \van^{n+1} & \mapsto 1.
\end{split}\end{equation*}
When $b$ is a branch point, the coordinate $\omega_b$ we fixed in ``A sense of direction'' gives us an isomorphism
\begin{equation*}\begin{split}
w_b \maps T^*_bB & \to \C \\
\omega_b + \van^2 & \mapsto 1
\end{split}\end{equation*}
that makes the diagram
\begin{center}
\begin{tikzcd}
T^*_bB^{\otimes n} \arrow[r,"z"] & \C \\
T^*_bB \arrow[u,"\blankbox^n"] \arrow[r,"w"'] & \C \arrow[u,"\blankbox^n"']
\end{tikzcd}
\end{center}
commute. Here, $\blankbox^n$ represents the $n$th-power map.
%
\subsubsection{The Laplace transform over an ordinary point}\label{laplace:ordinary}
%
Pick a translation parameter $\zeta$ on $B$ and an extended angle $\theta \in \R$. The {\em Laplace transform} $\laplace_{\zeta, \alpha}^\theta$ turns a local holomorphic function $\phi$ on $B$ into a local holomorphic function on $T^*_{\zeta = 0} B$. When $\zeta = 0$ is an ordinary point, the Laplace transform is defined by the formula
\begin{equation}\label{laplace:int}
\laplace_{\zeta, \alpha}^\theta \phi = \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta} \phi\,d\zeta,
\end{equation}
where $z$ is the frequency function and $\mathcal{J}_{\zeta, \alpha}^\theta$ is the ray $\zeta \in \alpha + e^{i\theta} [0, \infty)$. To make sense of this formula, we ask for the following conditions.
\begin{itemize}
\item The starting point $\zeta = \alpha$ is in the domain of $\zeta$. Once we have this, we can continue $\zeta$ along the whole ray $\mathcal{J}_{\zeta, \alpha}^\theta$.
\item The ray $\mathcal{J}_{\zeta, \alpha}^\theta$ avoids the branch points after leaving $\zeta = \alpha$.
\item The integral converges. We ensure this by putting conditions on $\phi$ and $z$.
\begin{itemize}
\item With respect to the flat metric, $\phi$ is uniformly of exponential type $\Lambda$ along the ray $\mathcal{J}_{\zeta, \alpha}^\theta$, and is locally integrable throughout the ray.\footnote{Recall that a function $\phi$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|\phi|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$. We instead require a uniform constant $A$ such that $|\phi| \le A e^{\Lambda|\zeta|}$.}
\item The value of $z$ satisfies the inequality $\Re(e^{i\theta} z) > \Lambda$, which cuts out a half-plane $H^\theta_\Lambda$ in $T^*_{\zeta = 0} B$.
\end{itemize}
\end{itemize}
For any $\sigma > -1$, the conditions on $\phi$ are satisfied by all of the functions in the spaces $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ introduced in \cite[Definition~2.3]{reg-sing-volterra}. Here, the domain $\Omega_\alpha$ must contain the ray $\mathcal{J}_{\zeta, \alpha}^\theta$, and the norm $\|\cdot\|_{\sigma, \Lambda}$ is taken with respect to $\zeta = \alpha$.

@@

\[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|. \]       

@@

    e^{-z\alpha} \laplace_{\zeta_\alpha, 0} \varphi = \laplace_{\zeta, \alpha} \varphi.

@@

& = e^{-z\alpha } \laplace_{\zeta_\alpha, 0} \varphi.

@@

    \[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]

@@

\[\borel_{\zeta_\alpha}\Big[e^{z\alpha} \laplace_{\zeta,\alpha}\big[\zeta^n\big]\Big]=\zeta^n.\]

@@

      &=\zeta^n.

@@

& = \int_{\mathcal{N}_{\zeta, \alpha, \beta}} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{z\zeta(a')}\,\psi(a')\,d\zeta(a') \right].

@@

\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha,\beta}{\psi}] = \left[ \int_{\mathcal{J}_{\zeta, \alpha}} e^{-z\zeta}\,\phi\,d\zeta \right] \left[ \int_{\mathcal{J}_{\zeta,\beta}} e^{-z\zeta}\,\psi\,d\zeta \right]. \]

@@

If a function on $\Omega$ has an ordinary Taylor expansion in $\C\{\zeta\}$, summing the series extends the function to a neighborhood of $\zeta = 0$. The subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the ordinary Taylor series exists can thus be seen as the intersection
\[ \mathcal{O}_{\zeta = \alpha} \cap \singexp{\sigma}{\Lambda}(\Omega), \]
where $\mathcal{O}_{\zeta = \alpha}$ is the algebra of germs of holomorphic functions at $\zeta$. More generally, for any $\rho \ge \sigma$, the subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the $\rho$-shifted Taylor series exists can be seen as the intersection
\[ \zeta^\rho\,\mathcal{O}_{\zeta = \alpha} \cap \singexp{\sigma}{\Lambda}(\Omega). \]

>>>>

% Address of Second Author
\Address{$^{\rm b)}$~Studio Infinity, USA}
\EmailD{\href{mailto:aaron.fenyes@fareycircles.ooo}
{aaron.fenyes@fareycircles.ooo}} % E-mail address of Second Author
\URLaddressD{\url{https://ooo.fareycircles.ooo}} %URL address of Second Author

@@

%
\section{Introduction}
%
\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
You can often find a formal power series
\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots\,, \]
with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
\begin{equation}
\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0\,. \label{eqn:bessel_rescaled_ex}
\end{equation}
behave near $z = \infty$, you might start by looking for formal {\em trans-monomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.\footnote{Trans-mononials can be of different kinds: for example, fractional powers of $z$ can appear in the exponential. In this paper, however, we will only deal with trans-monomials of the form $e^{-\alpha z}\,\series{\Phi}$ for $\alpha \in \C$.} Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution 
\begin{equation}
e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{6718464} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel_ex}
\end{equation}
and its constant multiples (see \cite[equation 10.40.1]{dlmf}). As another example, you might rewrite the integral
\begin{equation}\label{int:bessel_ex}
\Phi = \int_{\mathcal{C}} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du
\end{equation}
as
\[ e^{z}\, \frac{1}{2\sqrt{3}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{\sqrt{3}}{9} t + \frac{5}{72} t^2 - \frac{4\sqrt{3}}{243} t^3 + \frac{385}{31104} t^4 - \frac{7\sqrt{3}}{2187} t^5 + \frac{17017}{6718464} t^6 - \ldots \right] dt \]
using the substitution $\tfrac{1}{2} t^2 = 4u^3 - 3u + 1$. Na\"{i}vely integrating term by term, you again get the trans-monomial~\eqref{series:bessel_ex}, up to a constant.

@@

The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
\begin{enumerate}
\item Solving a level~$1$ linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.\footnote{Calling a linear ODE {\em level~$1$} is a short way of saying that it has ``a single level, equal to $1$, at infinity.'' That means a certain Newton polygon associated with its singularity at infinity has exactly one positive-slope side, which has slope~$1$. In general, the {\em levels} of a linear ODE at a given singularity are the slopes of the positive-slope sides of the associated Newton polygon~\cite[Proposition~3.3.14]{diverg-resurg--ii}.} Equation~\eqref{eqn:bessel_rescaled_ex} is an example. More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form 
\[ \mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1})\,, \]
where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial that is non-zero at every root of $P$, and $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. We will restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}), and to the solutions associated with roots $-\alpha$ where $\tau_\alpha:=\frac{Q(-\alpha)}{P'(-\alpha)}$ is real and positive (see Theorem~\ref{thm:exist_uniq_ODE}).

The form of $\mathcal{P}$ derives from equation~2.2.3 of \cite[p.~105]{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$. Borel summation is more involved for the nonlinear ones, raising the question of whether our analysis generalizes.
%
\item Evaluating a one-dimensional {\em thimble integral}. Integral~\eqref{int:bessel_ex} is an example. More generally, we will consider integrals of the form
\begin{equation*}
I = \int_{\mathcal{C}}e^{-zf}\,\nu\,,
\end{equation*}
where $X$ is one-dimensional complex manifold; $f \maps X \to \C$ is a holomorphic function with isolated, non-degenerate critical points; $\nu \in \Omega^1(X)$ is holomorphic $1$-form on $X$, and $\mathcal{C}$ is {\em Lefschetz thimble}---a type of contour described in Section~\ref{sec:why_borel_thimble}. Under these conditions, $I$ is a holomorphic function of $z$.
\end{enumerate}
These two problems are closely linked. By playing with derivatives of a thimble integral, you can often find a linear ODE that the integral satisfies. Conversely, for many classical ODEs, there are useful bases of thimble integral solutions.
%
\subsection{Goals and Results}
%
We present the results, proofs, and examples in this paper with a few central goals in mind. Our first goal is to discuss Borel summability in a way that carefully separates the analytic and formal sides of the theory. In particular, we highlight results that can be proven in purely analytic ways, like Theorem~\ref{thm:exist_uniq_ODE} for level~$1$ ODEs and Lemma~\ref{lem:thimble_proj_formula} for thimble integrals.

@@

We are now ready to define a one-dimensional thimble integral precisely, at our desired level of generality.
\begin{definition}
Fix a one-dimensional complex manifold $X$; a translation surface $B$; and a holomorphic map $f \maps X \to B$ with isolated, non-degenerate critical points. A one-dimensional {\em thimble integral} has the form
\[ I_a = \int_{\mathcal{C}_a^\theta} e^{-zf}\,\nu\,, \]
where $\nu$ is a holomorphic $1$-form on $X$, $a$ is a critical point of $f$, and $\mathcal{C}^\theta_a$ is the Lefschetz thimble that runs through $a$ in direction $\theta$ with a chosen orientation. Since $I_a$ depends on the frequency coordinate $z$, it is a holomorphic function on the frequency domain.
\end{definition}
We will present a proof that one-dimensional thimble integrals are always Borel regular. The proof hinges on the following well-known formula, which can be used to express any one-dimensional thimble integral as a Laplace transform.
\begin{lemma}[adapted from {\cite[Section~3.3]{pham}}]\label{lem:thimble_proj_formula}
A function $\iota_a$ with $I_a = \laplace_{\zeta, \alpha}^\theta \iota_a$ is given by the {\em thimble projection formula}
\begin{equation}\label{eqn:formula}
    \iota_a = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right)\,,
\end{equation}
where $\mathcal{C}_a^\theta(\zeta)$ is the part of $\mathcal{C}_a^\theta$ that goes through $f^{-1}([\alpha,\zeta e^{i\theta}])$.
\end{lemma}
Notice that the path $\mathcal{C}_a^\theta(\zeta)$ used in the lemma starts and ends in $f^{-1}(\zeta)$.

@@

In the path integral picture of quantum mechanics, which draws inspiration from wave optics, infinite-dimensional thimble integrals are supposed to give the expectation values of observable quantities. In this context, the integral's formal asymptotic expansion is often better-defined than the integral itself, so physicists use Borel summation, resurgence, and related techniques to assign the integral a value. For instance, in the two-dimensional, $\mathcal{N}=2$ supersymmetric QFTs given by Landau--Ginzburg theories, Cecotti and Vafa showed that instantons can be computed using Picard--Lefschetz formulas. Indeed, the so-called wall-crossing phenomenon is equivalent to the Stokes phenomenon for thimble integrals~\cite{Cecotti:1992rm}. Similarly, in complex Chern--Simons theory, the path integral can be studied by decomposing it into thimble integrals and then arguing as in finite dimension~\cite{gukov-marino-purtrov-resurgence,Witten}. Other examples can be found in~\cite{costin_kruskal,Garoufalidis--CS,GTM--CS,GGM,dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua,Berry_Howls,Berry1991,Howls97,Howls,pham1988resurgence,Unsal--resurgence-gauge}.
%
\subsubsection{Thimble integrals in geometry}
Thimble integrals can be used to explore the geometry of complex manifolds, and even to represent elements of a homology group. To see how this works, we first recall how the one-dimensional definition of a Lefschetz thimble arises from the general definition. Suppose that $f \maps X \to B$ is a holomorphic map from an $N$-dimensional complex manifold $X$ to a translation surface $B$. Consider a translation chart $\zeta$ on $B$ and a non-degenerate critical point $a \in X$ that $f$ sends to $\zeta = \alpha$. Near $a$, we can always find coordinates $t_1, \ldots, t_N$ on $X$ with
\[ f^*\zeta = \alpha + e^{i \theta} (t_1^2 + \ldots + t_N^2)\,. \]
When the ray $\mathcal{J}_{\zeta, \alpha}^\theta$ avoids the other critical values of $f$, each such coordinate system defines a Lefschetz thimble: the oriented real-analytic submanifold where $t_1, \ldots, t_N$ are real. There are many such coordinate systems, but they are all related by local holomorphic maps from $X$ to the complex orthogonal group $O_N(\C)$. Since $O_N(\C)$ has only two connected components, distinguished by the sign of the determinant, a Lefschetz thimble is determined up to homotopy and orientation by the critical point $a$ and the direction $\theta$. When $N = 1$, the homotopy freedom disappears, because $O_1(\C)$ is the discrete group $\{\pm 1\}$.

@@

At an ordinary point, we can define $z$ simply as the map
\begin{equation*}
\begin{split}
z \maps T^*_bB & \to \C \\
\lambda\big|_b & \mapsto 1\,.
\end{split}
\end{equation*}
To generalize $z$ to branch points, though, we need a more sophisticated definition. Recall that $T^*_bB = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$. Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*_bB^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$. When $b$ is an ordinary point, the translation parameter $\zeta_b$ that vanishes at $b$ represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda\big|_b$. In general, $\zeta_b$ represents a nonzero element of $\van_b^n / \van_b^{n+1}$, where $2\pi n$ is the cone angle at $b$. We define $z$ as the isomorphism
\begin{equation*}\begin{split}
z \maps \van_b^n / \van_b^{n+1} & \to \C \\
\zeta_b + \van^{n+1} & \mapsto 1\,.
\end{split}\end{equation*}
When $b$ is a branch point, the coordinate $\omega_b$ we fixed in ``A sense of direction'' gives us an isomorphism
\begin{equation*}\begin{split}
w_b \maps T^*_bB & \to \C \\
\omega_b + \van^2 & \mapsto 1
\end{split}\end{equation*}
that makes the diagram
\begin{center}
\begin{tikzcd}
T^*_bB^{\otimes n} \arrow[r,"z"] & \C \\
T^*_bB \arrow[u,"\blankbox^n"] \arrow[r,"w"'] & \C \arrow[u,"\blankbox^n"']
\end{tikzcd}
\end{center}
commute. Here, $\blankbox^n$ represents the $n$th-power map.
%
\subsubsection{The Laplace transform over an ordinary point}\label{laplace:ordinary}
%
Pick a translation parameter $\zeta$ on $B$ and an extended angle $\theta \in \R$. The {\em Laplace transform} $\laplace_{\zeta, \alpha}^\theta$ turns a local holomorphic function $\phi$ on $B$ into a local holomorphic function on $T^*_{\zeta = 0} B$. When $\zeta = 0$ is an ordinary point, the Laplace transform is defined by the formula
\begin{equation}\label{laplace:int}
\laplace_{\zeta, \alpha}^\theta \phi = \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta} \phi\,d\zeta\,,
\end{equation}
where $z$ is the frequency function and $\mathcal{J}_{\zeta, \alpha}^\theta$ is the ray $\zeta \in \alpha + e^{i\theta} [0, \infty)$. To make sense of this formula, we ask for the following conditions.
\begin{itemize}
\item The starting point $\zeta = \alpha$ is in the domain of $\zeta$. Once we have this, we can continue $\zeta$ along the whole ray $\mathcal{J}_{\zeta, \alpha}^\theta$.
\item The ray $\mathcal{J}_{\zeta, \alpha}^\theta$ avoids the branch points after leaving $\zeta = \alpha$.
\item The integral converges. We ensure this by putting conditions on $\phi$ and $z$.
\begin{itemize}
\item With respect to the flat metric, $\phi$ is uniformly of exponential type $\Lambda$ along the ray $\mathcal{J}_{\zeta, \alpha}^\theta$, and is locally integrable throughout the ray.\footnote{Recall that a function $\phi$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|\phi|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$. We instead require a uniform constant $A$ such that $|\phi| \le A e^{\Lambda|\zeta|}$.}
\item The value of $z$ satisfies the inequality $\Re(e^{i\theta} z) > \Lambda$, which cuts out a half-plane $H^\theta_\Lambda$ in $T^*_{\zeta = 0} B$.
\end{itemize}
\end{itemize}
For any $\sigma > -1$, the conditions on $\phi$ are satisfied by all of the functions in the spaces $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ introduced in \cite[Definition~2.3]{reg-sing-volterra}. Here, the domain $\Omega_\alpha$ must contain the ray $\mathcal{J}_{\zeta, \alpha}^\theta$, and the norm $\|\cdot\|_{\sigma, \Lambda}$ is taken with respect to $\zeta = \alpha$.

@@

\[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|\,. \]       

@@

    e^{-z\alpha} \laplace_{\zeta_\alpha, 0} \varphi = \laplace_{\zeta, \alpha} \varphi\,.

@@

& = e^{-z\alpha } \laplace_{\zeta_\alpha, 0} \varphi\,.

@@

    \[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi\,. \]

@@

\[\borel_{\zeta_\alpha}\Big[e^{z\alpha} \laplace_{\zeta,\alpha}\big[\zeta^n\big]\Big]=\zeta^n\,.\]

@@

      &=\zeta^n\,.

@@

& = \int_{\mathcal{N}_{\zeta, \alpha, \beta}} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.

@@

\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha,\beta}{\psi}] = \left[ \int_{\mathcal{J}_{\zeta, \alpha}} e^{-z\zeta}\,\phi\,d\zeta \right] \left[ \int_{\mathcal{J}_{\zeta,\beta}} e^{-z\zeta}\,\psi\,d\zeta \right]\,. \]

@@

If a function on $\Omega$ has an ordinary Taylor expansion in $\C\{\zeta\}$, summing the series extends the function to a neighborhood of $\zeta = 0$. The subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the ordinary Taylor series exists can thus be seen as the intersection
\[ \mathcal{O}_{\zeta = \alpha} \cap \singexp{\sigma}{\Lambda}(\Omega)\,, \]
where $\mathcal{O}_{\zeta = \alpha}$ is the algebra of germs of holomorphic functions at $\zeta$. More generally, for any $\rho \ge \sigma$, the subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the $\rho$-shifted Taylor series exists can be seen as the intersection
\[ \zeta^\rho\,\mathcal{O}_{\zeta = \alpha} \cap \singexp{\sigma}{\Lambda}(\Omega)\,. \]
